\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xcolor}

\title{SE 3XA3: Problem Statement\\Othello}

\author{Team \# 02, JMS Corporation
		\\ Jinesh Patel - patelj60
		\\ Sankar Renganthan - renganas
		\\ Mohammed Mirajkar - mirajkam
}

\date{Sep 21, 2018}
	
%\input{../Comments}
	
\begin{document}

\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}         \\
		\midrule
		19/9/18       & Sankar Renganathan    & Context, Problem        \\
		19/9/18       & Mohammed Mirajkar     & Problem, Edited Context \\
		19/9/18       & Jinesh Patel          & Revised Document        \\
		\bottomrule
	\end{tabularx}
\end{table}

\newpage

\maketitle

\section{Problem}
People around the world struggle to find entertainment in their lives and they often turn to other means of entertainment such as television and board games to distract themselves. Board games are very enjoyable but they require many components to play properly, such as, the game pieces and the game board, which can be a hassle to transport. {\color{blue} Additionally, most board games require two or more players which makes it incredibly hard to play board games by oneself . Othello is a popular board game that requires many pieces to play that can often get lost and render the game unplayable. An online implementation of othello will make it much easier to play othello, without having to worry about losing any pieces or transporting the game board. All you need to play is a computer and  internet connection is not required. Moreover, it is possible to play against the computer in an online version of othello compared to playing othello in real life.}


\section{Context}

The main stakeholders for Othello are the users who play the game. The software will be implemented as a web application, allowing for easy access for users willing to play the game on a variety of platforms, such as a desktop computer or a mobile phone. Developers can maintain the game by creating bug fixes as well as minor enhancements to the code. This will help the user's experience with playing the game over time.

\section{Significance of the solution}

The importance of the problem to the stakeholders is to help enhance their experience with gaming and to help them enjoy their time. By creating an online version of Othello, the process of playing board games will be easier and straightforward. The implementation will allow users to experience smooth gameplay and flexible gaming options to fit their playstyle anywhere and anytime they like. The end result will have users conveniently pass the time when they are bored as well being able to test their minds based on the strategic gameplay.


%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}